Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-16 cikm2016/intro.tex
Fixed orphan lines

The SQL-99 standard defines three temporal scalar types: \functionname{DATE}, \functionname{TIMESTAMP} and \functionname{TIME}, 
which can be further qualified as either \functionname{WITH} or \functionname{WITHOUT} \functionname{TIME ZONE} (the \functionname{WITHOUT} form being more common.) 
These types are typically implemented as fixed-point offsets from some epoch (\textit{e.g.}, Julian Days.) 
This makes them compact to store using columnar compression techniques such as those in C-Store~\cite{Stonebraker:2005} and MonetDB/X100~\cite{Zukowski:2006}, 
and further allows some temporal operations to be implemented efficiently using simple arithmetic. 
Thus from the RDBMS perspective, representing dates in scalar form provides benefits for users, both in terms of analytic richness and query performance.

>>>>

The SQL-99 standard defines three temporal scalar types: \functionname{DATE}, \functionname{TIMESTAMP} and \functionname{TIME}, 
which can be further qualified as either \functionname{WITH} or \functionname{WITHOUT} \functionname{TIME ZONE} (the \functionname{WITHOUT} form being more common.) 
These types are typically implemented as fixed-point offsets from some epoch (\textit{e.g.}, Julian Days.) 
This makes them compact to store using columnar compression techniques such as those in C-Store~\cite{Stonebraker:2005} and MonetDB/X100~\cite{Zukowski:2006}, 
and further allows some temporal operations to be implemented efficiently using simple arithmetic. 
Thus from the RDBMS perspective, representing dates in scalar form provides benefits for users, both in terms of analytic richness and query performance.\\
